---
title: "Usage of inferCSN with Seurat object"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{usages_seurat}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Load the necessary libraries and data.

```{r setup}
library(BSgenome.Hsapiens.UCSC.hg38)
library(inferCSN)
data(motifs)
```

Simulate data and create a `Seurat` object.

```{r}
sim_data <- simulate_csn_data()
seurat_object <- create_seurat_object(sim_data)
```

Initiate the `Seurat` object to `CSNObject` containing peak data.

```{r}
object <- initiate_object(
  seurat_object,
  peak_assay = "ATAC",
  celltype_by = "celltype"
)
```

The `find_motifs` function is used to find motifs for `CSNObject` when provided peak data. But it could run without peak data as well, and will return the object without any changes.

```{r}
object <- find_motifs(
  object,
  pfm = motifs,
  genome = BSgenome.Hsapiens.UCSC.hg38
)
```

Initiate the `Seurat` object to `CSNObject` without peak data.

```{r}
object <- initiate_object(
  seurat_object,
  celltype_by = "celltype"
)
```

The `find_motifs` function is used to find motifs for `CSNObject` when provided peak data. But it could run without peak data as well, and will return the object without any changes.

```{r}
object <- find_motifs(
  object,
  pfm = motifs,
  genome = BSgenome.Hsapiens.UCSC.hg38
)
```

The `inferCSN` function is used to infer the CSN for the given celltypes, regulators and targets.

```{r}
object <- inferCSN(
  object,
  n_cores = 1
)
```

Export the inferred CSN as a network.

```{r}
networks <- export_csn(
  object
)
head(networks[[1]])
```
